---
title: "hw_06"
author: "lisa liubovich"
date: "2024-03-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loans

## 1.

```{r l1}
y <- c(16, 5, 10, 15, 13, 22)
y
```

## 2.

```{r l2}
X <- matrix(c(1, 4,
              1, 1,
              1, 2,
              1, 3,
              1, 3,
              1, 4), ncol = 2, nrow = 6, byrow = TRUE)
X
```

## 3.

Beta-hat = (XTX)^-1^ \* (XTY)

```{r l3}
betahat = solve(t(X) %*% X) %*% t(X) %*% y
betahat
```

## 4.

s^2^ (beta hat) = MSE (XTX)^-1^

with help from ChatGPT: <https://chat.openai.com/c/6e20bc4c-a72c-4ab5-a278-0c5ff4fe543e>

```{r l4}
y_pred <- X %*% betahat
residuals <- y - y_pred
df <- length(y) - ncol(X)
MSE <- sum(residuals^2)/df
MSE
```

## 5.

s^2^ (beta hat) = MSE (XTX)^-1^

with help from ChatGPT: <https://chat.openai.com/c/6e20bc4c-a72c-4ab5-a278-0c5ff4fe543e>

```{r l5}
cov_matrix <- MSE * solve(t(X) %*% X)
variances <- diag(cov_matrix)
SE_beta <- sqrt(variances)
SE_beta
```

## 6.

```{r l6}
summary(lm(y ~ X[, 2]))
```

# Other questions

## 1.

system of equations in matrix notation is: W = AY

where:

W = [ W1 W2 W3], Y = [ Y1 Y2 Y3}

(imagine these are vertical, I just can't figure out how to make it that way in R, sorry!)

coefficient matrix A: (again, imagine there are brackets around this)

1 -1 2

A = 0 0 -1

1 0 0

so the system of linear equations can be represented as (imagine brackets, sorry)

W1 0 -1 2 Y1

W2 = 0 1 1 Y2

W3 1 0 0 Y3

## 2.

AB11 = 1(2) + 3(1) + 5(3) = 2 + 3 + 15 = 20

AB12 = 1(-2) + 3(-1) + 5(-3) = -2 - 3 - 15 = -20

AB21 = 2(2) + 4(1) + 6(3) = 4 + 4 + 18 = 26

AB22 = 2(-2) + 4(-1) + 6(-3) = -4 -4 - 18 = -26

so the resulting matrix AB is:

20 -20

26 -26

Verifying with R:

```{r oq2}
A <- matrix(c(1, 3, 5, 2, 4, 6), nrow = 2, byrow = TRUE)
B <- matrix(c(2, -2, 1, -1, 3, -3), nrow = 3, byrow = TRUE)

AB <- A %*% B
AB
```
