---
title: "Predictors"
author: "David Gerard"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
library(broom)
muscle <- read_csv("https://dcgerard.github.io/stat_415_615/data/muscle.csv")
glimpse(muscle)
```

```{r}
muscle <- mutate(muscle, age2 = age^2)
lm_quad <- lm(mass ~ age + age2, data = muscle)
tidy(lm_quad)
```
Do we have evidence of curvature? We have very weak evidence (p = 0.081)

If we have a quadratic model we are happy with and we want to evaluate if age is associated with mass.
```{r}
glance(lm_quad)
```
We have very strong evidence of an association between age and mas (p = 1.5e-18)

We can look at the scatterplot
```{r}
ggplot(muscle, aes(x = age, y = mass)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE,
              formula = y ~ x + I(x^2))
```

```{r}
lm_quad2 <- lm(mass ~ age + I(age^2), data = muscle)
tidy(lm_quad2)
```

We want to predict at age = 45
```{r}
newdf <- data.frame(age = 45, age2 = 45^2)
predict(lm_quad, newdf)
```

```{r}
newdf <- data.frame(age = 45)
predict(lm_quad2, newdf)
```

# Splines

```{r}
library(splines)
ggplot(muscle, aes(x = age, y = mass)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE,
              formula = y ~ bs(x, df = 4))
```


We can fit a spline relationship between age and mass
```{r}
lm_spline <- lm(mass ~ bs(age, df = 4), data = muscle)
tidy(lm_spline)
```

We can use this spline model to see if there is a relationship between age and mass
```{r}
glance(lm_spline)
```

We can use it as a full model to see if there is evidence of curvature
```{r}
lm_reduced <- lm(mass ~ age, data = muscle)
anova(lm_reduced, lm_spline)
```


# Categorical variables

```{r}
firm <- read_csv("https://dcgerard.github.io/stat_415_615/data/firm.csv")
glimpse(firm)
```


```{r}
ggplot(firm, aes(x = size, y = months, color = type)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
lm_firm1 <- lm(months ~ type + size, data = firm)
tidy(lm_firm1)
```

What if I wanted x1 to be an indicator for mutuals, not stocks. What would be the coefficient estimate corresponding to that indicator?


```{r}
firm <- mutate(firm,
               type = factor(type),
               type = fct_relevel(type, "stock"))
lm_firm2 <- lm(months ~ type + size, data = firm)
tidy(lm_firm2)
```

```{r}
tidy(lm_firm1)
```


Q: How long did a stock insurance company with $100 million revenue take to adopt the "innovation". Provide a measure of uncertainty.

The estimated number of months is
```{r}
33.87 + 8.0555 - 0.1017 * 100

newdf <- data.frame(type = "stock", size = 100)
predict(lm_firm1, newdf, interval = "prediction")
```
We predict such a company will take 32 months (95% prediction interval of 24.4 to 39.1 months)

We need to check for normality to verify that we can do a prediction interval
```{r}
aout <- augment(lm_firm1)
ggplot(aout, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0)

ggplot(aout, aes(sample = .resid)) +
  geom_qq() +
  geom_qq_line()
```


```{r}
# Don't use these in a HW (ugly)
plot(lm_firm1)
```




# Three classes

```{r}
data("mpg")
lm_mpg <- lm(cty ~ drv + displ, data = mpg)
tidy(lm_mpg)
```

```{r}
mpg <- mutate(mpg, drv = factor(drv),
              drv = fct_relevel(drv, "r", "f", "4"))
lm_mpg2 <- lm(cty ~ drv + displ, data = mpg)
tidy(lm_mpg2)
```

Q: What is the expected mpg for 4-wheel drive cars with 2L engines?
```{r}
26.1841 - 2.5045 - 2.3385 * 2

newdf <- data.frame(drv = "4", displ = 2)
predict(lm_mpg2, newdf)
```

# Interactions

Let's fit an interaction effect in a model between mpg (Y) and drat (X1) and wt (X2)
```{r}
data("mtcars")
lm_int1 <- lm(mpg ~ drat + wt + drat:wt, data = mtcars)
tidy(lm_int1)
```


# Interaction between categorical and quantitative

```{r}
ggplot(mpg, aes(x = displ, y = cty, color = drv)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
lm(cty ~ drv + displ + drv:displ, data = mpg)

## A little less prone to error
lm_int <- lm(cty ~ drv * displ, data = mpg)
tidy(lm_int)
```


Let's test for the interaction
```{r}
lm_red <- lm(cty ~ drv + displ, data = mpg)
anova(lm_red, lm_int)
```

We have strong evidence of an interaction effect between engine displacement and drive type (p = 0.00012).

```{r}
library(car)
Anova(lm_int)
```

# Second order saturated model
```{r}
power <- tibble::tribble(
  ~cycles, ~charge, ~temp,
      150,     0.6,    10,
       86,       1,    10,
       49,     1.4,    10,
      288,     0.6,    20,
      157,       1,    20,
      131,       1,    20,
      184,       1,    20,
      109,     1.4,    20,
      279,     0.6,    30,
      235,       1,    30,
      224,     1.4,    30
  )
```

```{r}
library(GGally)
power <- relocate(power, cycles, .after = everything())
ggpairs(power)
```


```{r}
lm_lin <- lm(cycles ~ charge + temp, data = power)
plot(lm_lin) ## looks OK
```

Let's fit a saturated model
```{r}
lm_quad <- lm(cycles ~ charge * temp + I(charge^2) + I(temp^2), data = power)
anova(lm_lin, lm_quad)
```

```{r}
library(tidyverse)
library(broom)
soap <- read_csv("https://dcgerard.github.io/stat_415_615/data/soap.csv")
glimpse(soap)
```


```{r}
ggplot(soap, aes(x = speed, y = scrap, color = line)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

Let $X_{i1}$ be an indicator for line 2.

$Y_i = \beta_0 + \beta_1X_{i1} + \beta_2X_{i2} + \beta_{12}X_{i1}X_{i2} + \epsilon_i$

```{r}
lm_int <- lm(scrap ~ line * speed, data = soap)
tidy(lm_int)
```

```{r}
plot(lm_int)
```

```{r}
tidy(lm_int)
```

We do not have evidence of an interaction between speed an line 

(aka, we don't have evidence of different slopes)

Let's fit the model without interactions
```{r}
lm_soap <- lm(scrap ~ line + speed, data = soap)
tidy(lm_soap, conf.int = TRUE)
```

We have strong evidence that the lines produce different scrap amounts, adjusting for speed, on average (p = 1.082e-6). We estimate that line 2 produces on average 53.129 less scrap than line one when production is at the same speed (95% CI of 36.185 to 70.074 less scrap).







