---
title: "exclusive_breastfeeding_models"
author: "remy sorensen"
date: "`r Sys.Date()`"
output: html_document
---
```{r}
library(tidyverse)
library(broom)
library(GGally)
library(stats)
```

```{r}
niger <- read_csv("CLEANNigerData.csv")
niger
```
Logistic Regression Formula:
= beta0 + beta1 * X1 + beta2 * X2 + beta3 * X3 + beta4 * Z1 + beta5 * Z2 + beta6 * Z3



# EXCLUSIVE BREASTFEEDING 

3 models: all three models use all gateway factors, model 1 uses any ANC from gateway behaviors, model 2 uses facility delivery from gateway behaviors, and model 3 uses all three variables from communication on child nutrition. the goal is to find the odds ratio (OR) and confidence interval (CI). 

n = 652
models control for: women's age, parity, educational attainment, household wealth tercile
Dependent Variable: Breastfeeding for 0-5 month old children 

variables used:
- gateway factors: 
  - breastfeeding behavioral determinants: att_1, know_1, se_3, pn_1
  - exposure to breastfeeding messages in the last 3 months: exp
  - gender decision-making: decision_combined
  - womens group participation: wg
- gateway behaviors: antenatal, fac_delivery, nutrition
- controls: age, parity, any_edu, wealth


variable key:

-   any_edu: percentage of MWRA who reported to have ever gone to school
    -   binary variable
    -   0 - no, 1 - yes
    
-   parity: Percentage of MRWA who reported living children and grouped (0 children, 1-2 children, 3-4 children, 5-6 children, and 7+ children)
    -   categorical variable
    -   4 levels: 1-2 children, 3-4 children, 5-6 children, 7+ children
    
-   age: percentage of MWRA who reported their current age and grouped
    -   factor with 3 levels:
    -   15 to 24 years
    -   25 to 34 years
    -   35 to 49 years
    
-   nutrition: percentage of MWRA who spoke with 1) husband/partner, 2) family member, 3) health provider, 4) nobody about child's nutrition

-   att_1: attitude gateway 1; percentage of MWRA who agree if a baby is exclusively breastfed for 6 months, he/she is less likely to be sick
    -   binary variable
    -   1 = those who agree that if a baby is exclusively breastfed for 6 months, they are less likely to get sick, 0 = otherwise
    
-   know_1: knowledge gateway 1; percentage of MRWA who state it is healthy for a woman to give only breast milk for the first 6 months
    -   binary variable
    -   1 = those who agree it is healthy for a woman to give a child only breastmilk for the first 6 months, 0 otherwise
    
-   wealth: percentage of MWRA who reported household assets constructed in wealth terciles
    -   1 = poorest tercile
    -   2 = middle
    -   3 = richest
    
-   se_3: self-efficacy gateway 3; percentage of MRWA who say giving a child a minimum of 4 or more different types of food a day is not difficult at all
    -   binary variable
    -   1 = those who agree that giving a child a minimum of 4 or more different types of food a day is not difficult at all, 0 = otherwise

-   se_1: self-efficacy gateway 1; percentage of MWRA who agree giving only breast milk to the baby for the first 6 months is not difficult at all
    -   binary variable
    -   1 = those who agree only giving breast milk to the baby for the first 6 months is not difficult at all, 0 = otherwise
    
-   pn_1 : perceived norms gateway 1; percentage of MRWA who agree people in the community think it is healthy for a woman to give her baby only breast milk for the first 6 months
    -   binary variable
    -   1 = those who agree people in the community think it is healthy for a woman to give her baby only breast milk for first 6 months, 0 = otherwise

-   exp: exposure to nutrition messages gateway; percentage of MWRA who had heard or seen a message related to breastfeeding or young child nutrition from the radio, health worker, or community event in the past 3 months
    -   1 = yes, 0 = no   

-   decision_combined: Percentage of MRWA who responded that she OR her and her partner jointly make decisions for all three categories: household purchases, healthcare, and visiting relatives
    -   binary variable
    -   1 = responded either decides herself or jointly with her partner on all three decision categories, 0 = otherwise

-   wg: Percentage of MRWA who belong to a women's community group
   
-   antenatal: antenatal care gateway behavior; percentage of MRWA who have given birth in the last 5 years and received antenatal care for their last pregnancy
    -   binary variable --\> not possible to be continuous
    -   1 = received antenatal care, 0 = otherwise  
    - (antenatal was recoded to received_antenatal_care)

-   fac_delivery: percentage of MWRA who have given birth in the years preceding the survey who delivered in a facility for their last birth
 
 
 
# MODEL 1

variables used:
- gateway factors: 
  - breastfeeding behavioral determinants: att_1, know_1, se_3, pn_1
  - exposure to breastfeeding messages in the last 3 months: exp
  - gender decision-making: decision_combined
  - womens group participation: wg
- gateway behaviors: antenatal (antenatal was recoded to received_antenatal_care)
- controls: age, parity, any_edu, wealth
- dependant variable(?): se_1


```{r}
model1 <- glm(se_1 ~ know_1 + att_1 + se_3 + pn_1 + exp + decision_combined + wg + received_antenatal_care + age + parity + any_edu + wealth, 
              data = niger, 
              family = binomial)

tidy(model1, conf.int = TRUE)
```
```{r}
# OR for model 1

odds_ratios_model1 <- exp(coef(model1))
odds_ratios_model1
```
```{r}
summary(model1)
```



# MODEL 2

variables used:
- gateway factors: 
  - breastfeeding behavioral determinants: att_1, know_1, se_3, pn_1
  - exposure to breastfeeding messages in the last 3 months: exp
  - gender decision-making: decision_combined
  - womens group participation: wg
- gateway behaviors: fac_delivery
- controls: age, parity, any_edu, wealth
- dependant variable(?): se_1


```{r}
model2 <- glm(se_1 ~ know_1 + att_1 + se_3 + pn_1 + exp + decision_combined + wg + fac_delivery + age + parity + any_edu + wealth, 
              data = niger, 
              family = binomial)

tidy(model2, conf.int = TRUE)
```
```{r}
# OR for model 2
odds_ratios_model2 <- exp(coef(model2))
odds_ratios_model2
```
```{r}
summary(model2)
```



# MODEL 3

variables used:
- gateway factors: 
  - breastfeeding behavioral determinants: att_1, know_1, se_3, pn_1
  - exposure to breastfeeding messages in the last 3 months: exp
  - gender decision-making: decision_combined
  - women's group participation: wg
- gateway behaviors: nutrition
- controls: age, parity, any_edu, wealth
- dependant variable(?): se_1


```{r}
model3 <- glm(se_1 ~ know_1 + att_1 + se_3 + pn_1 + exp + decision_combined + wg + nutrition + age + parity + any_edu + wealth, 
              data = niger, 
              family = binomial)

tidy(model3, conf.int = TRUE)
```



```{r}
#OR for model 3
odds_ratios_model3 <- exp(coef(model3))
odds_ratios_model3
```

```{r}
summary(model3)
```

