---
title: "min_dietary_diversity"
author: "remy sorensen"
date: "`r Sys.Date()`"
output: html_document
---
```{r}
library(tidyverse)
library(broom)
library(GGally)
library(stats)
```

```{r}
niger <- read_csv("CLEANNigerData.csv")
niger
```
# MINIMUM DIETARY DIVERSITY

Variables Used:
- gateway factors: 
     - minimun dietary diversity behavioral detriments: know_2, att_3, se_3, pn_3
     - exposure to nutritional messages: wg, decision_combined, exp
- gateway behaviors: antenatal, fac_delivery, nutrition
- controls: age, parity, any_edu, wealth
-response; know_3


Variable Key:

-   know 3: knowledge gateway 3; percentage of MWRA who reported that the number of different types of food a child 6-23 months should eat a day is 4 or more
    -   binary variable
    -   1 = those who agree a child 6-23 months should receive 4 or more different types of food, 0 = otherwise
    
-   pn_3: perceived norms gateway 3; percentage of MRWA who believes number of different types of food people in the community think a child 6-23 months should eat a day is 4 or more
    -   binary variable
    -   1 = those who believe the number of different types of food people in the community think a child 6-23 months should eat a day is 4 or more, 0 = otherwise
    
-   se_3: self-efficacy gateway 3; percentage of MRWA who say giving a child a minimum of 4 or more different types of food a day is not difficult at all
    -   binary variable
    -   1 = those who agree that giving a child a minimum of 4 or more different types of food a day is not difficult at all, 0 = otherwise
    
-   att_3: attitude gateway 3; percentage of MWRA who agree children who eat a variety of foods are less likely to get sick
    -   binary variable
    -   1 = those who agree children who eat a variety of foods are less likely to get sick
    
-   exp: exposure to nutrition messages gateway; percentage of MWRA who had heard or seen a message related to breastfeeding or young child nutrition from the radio, health worker, or community event in the past 3 months
    -   note: we are doing this bit differently than the authors because it was more simple and streamlined.

-   decision_combined: Percentage of MRWA who responded that she OR her and her partner jointly make decisions for all three categories: household purchases, healthcare, and visiting relatives
    -   binary variable
    -   1 = responded either decides herself or jointly with her partner on all three decision categories, 0 = otherwise

-   wg: Percentage of MRWA who belong to a women's community group
    -   1 belonged to a womens group, 0 otherwise

-   antenatal: antenatal care gateway behavior; percentage of MRWA who have given birth in the last 5 years and received antenatal care for their last pregnancy
    -   binary variable --\> not possible to be continuous
    -   1 = received antenatal care, 0 = otherwise

-   any_edu: percentage of MWRA who reported to have ever gone to school
    -   binary variable
    -   0 - no, 1 - yes
    
-   parity: Percentage of MRWA who reported living children and grouped (0 children, 1-2 children, 3-4 children, 5-6 children, and 7+ children)
    -   categorical variable
    -   4 levels: 1-2 children, 3-4 children, 5-6 children, 7+ children
    
-   age: percentage of MWRA who reported their current age and grouped
    -   factor with 3 levels:
    -   15 to 24 years
    -   25 to 34 years
    -   35 to 49 years
    
-   nutrition: percentage of MWRA who spoke with 1) husband/partner, 2) family member, 3) health provider, 4) nobody about child's nutrition

-   fac_delivery: percentage of MWRA who have given birth in the years preceding the survey who delivered in a facility for their last birth

-   wealth: percentage of MWRA who reported household assets constructed in wealth terciles
    -   1 = poorest tercile
    -   2 = middle
    -   3 = richest
    
-   know_2: knowledge gateway 2; percentage of MWRA who reported a child 6-23 months should eat 4 or more meals each day
    -   binary variable
    -   1 = those who agree a child 6-23 months should receive 4 or meals a day, 0 otherwise


# model 1
```{r}
model_diet_1 <- glm(know_3 ~ know_2 + att_3 + se_3 + pn_3 + wg + decision_combined + exp + received_antenatal_care + age + parity + any_edu + wealth,
                 data = niger, 
                 family = binomial)

tidy(model_diet_1, conf.int = TRUE)
```
```{r}
# OR for model 1

odds_ratios_model_diet_1 <- exp(coef(model_diet_1))
odds_ratios_model_diet_1
```
```{r}
summary(odds_ratios_model_diet_1)
```

# model 2
```{r}
model_diet_2 <- glm(know_3 ~ know_2 + att_3 + se_3 + pn_3 + wg + decision_combined + exp + fac_delivery + age + parity + any_edu + wealth,
                 data = niger, 
                 family = binomial)

tidy(model_diet_2, conf.int = TRUE)
```
```{r}
# OR for model 2

odds_ratios_model_diet_2 <- exp(coef(model_diet_2))
odds_ratios_model_diet_2
```
```{r}
summary(model_diet_2)
```




# model 3

```{r}
model_diet_3 <- glm(know_3 ~ know_2 + att_3 + se_3 + pn_3 + wg + decision_combined + exp + nutrition + age + parity + any_edu + wealth,
                 data = niger, 
                 family = binomial)

tidy(model_diet_3, conf.int = TRUE)
```


```{r}
# OR for model 3

odds_ratios_model_diet_3 <- exp(coef(model_diet_3))
odds_ratios_model_diet_3
```
```{r}
summary(model_diet_3)
```


