---
title: "Project Regression"
output: word_document
date: "2024-04-25"
---

```{r}
library(tidyverse)
library(broom)
library(GGally)
library(dplyr)

```


```{r}
NG <- read_csv("/Users/hawatoumbou/desktop/REG_615/CLEANNigerData.csv")
NG

```
Variables Model 1: 
- Gateway factors: 
- breastfeeding behavioral determinants: att_1, know_1, pn_1
  - att_1: attitude gateway 1; percentage of MWRA who agree if a baby is exclusively breastfed for 6 months, he/she is less likely to be sick
  - know_1: knowledge gateway 1; percentage of MRWA who state it is healthy for a woman to give only breast milk for the first 6 months
  - pn_1 : perceived norms gateway 1; percentage of MRWA who agree people in the community think it is healthy for a woman to give her baby only breast milk for the first 6 months


- exposure to breastfeeding messages in the last 3 months: exp
  -  exp: exposure to nutrition messages gateway; percentage of MWRA who had heard or seen a message related to breastfeeding or young child nutrition from the radio, health worker, or community event in the past 3 months
  
- gender decision-making: decision_combined
   - decision_combined: Percentage of MRWA who responded that she OR her and her partner jointly make decisions for all three categories: household purchases, healthcare, and visiting relatives
    
  
- womens group participation: wg
  - Percentage of MRWA who belong to a women's community group
  
- gateway behaviors: antenatal 
  -antenatal care gateway behavior; percentage of MRWA who have given birth in the last 5 years and received antenatal care for their last pregnancy


```{r}
model_1 <- glm( se_1 ~ know_1 + att_1 + pn_1 + exp + decision_combined + wg + received_antenatal_care, 
              family = binomial(link = "logit"), 
              data = NG)
model_1
tidy(model_1, conf.int = TRUE)

```
fitted regression surface=
logit$p_{i}$ = -0.9988 + 1.462$X_1$ - 0.03529$X_2$ -1.199$X_3$ + 1.866$X_4$ +0.1011$X_5$ + 0.2326$X_6$ +0.01295$X_7$
X1: knowledge gateway 
X2: Attitude gateway 
X3: Perceived Normal Gateway 
X4: Exposure 
X5: Decision Combined - decisions for all three categories: household purchases, healthcare, and visiting relatives
X6: Women's community group
X7: antenatal care 



Variables Model 2: 
- Gateway factors: 
- breastfeeding behavioral determinants: att_1, know_1, pn_1
  - att_1: attitude gateway 1; percentage of MWRA who agree if a baby is exclusively breastfed for 6 months, he/she is less likely to be sick
  - know_1: knowledge gateway 1; percentage of MRWA who state it is healthy for a woman to give only breast milk for the first 6 months
  - pn_1 : perceived norms gateway 1; percentage of MRWA who agree people in the community think it is healthy for a woman to give her baby only breast milk for the first 6 months


- exposure to breastfeeding messages in the last 3 months: exp
  -  exp: exposure to nutrition messages gateway; percentage of MWRA who had heard or seen a message related to breastfeeding or young child nutrition from the radio, health worker, or community event in the past 3 months
  
- gender decision-making: decision_combined
   - decision_combined: Percentage of MRWA who responded that she OR her and her partner jointly make decisions for all three categories: household purchases, healthcare, and visiting relatives
      -binary variable
        -  1 = responded either decides herself or jointly with her partner on all three decision categories, 0 = otherwise
  
- womens group participation: wg
  - Percentage of MRWA who belong to a women's community group
  
- gateway behaviors: facility delivery  
  - fac_delivery: percentage of MWRA who have given birth in the years preceding the survey who delivered in a facility for their last birth

```{r}
model_2 <- glm(se_1 ~ know_1 + att_1 + pn_1  + exp + decision_combined + wg + fac_delivery, 
              family = binomial(link = "logit"), 
              data = NG)

tidy(model_2, conf.int = TRUE)
```
logit$p_{i}$ = -2.104 + 1.512$X_1$ + 0.1733$X_2$ -1.065$X_3$ + 1.681$X_4$ +0.1139$X_5$ + 0.3802$X_6$ +1.403$X_7$
X1: knowledge gateway 
X2: Attitude gateway 
X3: Perceived Normal Gateway 
X4: Exposure 
X5: Decision Combined - decisions for all three categories: household purchases, healthcare, and visiting relatives
X6: Women's community group
X7: facility delivery





Variables Model 3: 
- Gateway factors: 
- breastfeeding behavioral determinants: att_1, know_1, pn_1
  - att_1: attitude gateway 1; percentage of MWRA who agree if a baby is exclusively breastfed for 6 months, he/she is less likely to be sick
  - know_1: knowledge gateway 1; percentage of MRWA who state it is healthy for a woman to give only breast milk for the first 6 months
  - pn_1 : perceived norms gateway 1; percentage of MRWA who agree people in the community think it is healthy for a woman to give her baby only breast milk for the first 6 months


- exposure to breastfeeding messages in the last 3 months: exp
  -  exp: exposure to nutrition messages gateway; percentage of MWRA who had heard or seen a message related to breastfeeding or young child nutrition from the radio, health worker, or community event in the past 3 months
  
- gender decision-making: decision_combined
   - decision_combined: Percentage of MRWA who responded that she OR her and her partner jointly make decisions for all three categories: household purchases, healthcare, and visiting relatives
    
  
- womens group participation: wg
  - Percentage of MRWA who belong to a women's community group
- gateway behaviors: nutrition  
```{r}
model3 <- glm(se_1 ~ know_1 + att_1  + pn_1 + exp + decision_combined + wg + nutrition,  
              family = binomial(link = "logit"), 
              data = NG)
tidy(model3, conf.int = TRUE)
```

logit$p_{i}$ = -0.967 + 1.471$X_1$ + -0.04103$X_2$ -1.205$X_3$ + 1.853$X_4$ +0.1002$X_5$ + 0.2391$X_6$ -0.00149$X_7$
X1: knowledge gateway 
X2: Attitude gateway 
X3: Perceived Normal Gateway 
X4: Exposure 
X5: Decision Combined - decisions for all three categories: household purchases, healthcare, and visiting relatives
X6: Women's community group
X7: Communication about nutrition 

