---
title: "class_3_20_anova"
author: "lisa liubovich"
date: "2024-03-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sum of Squares

```{r}
library(tidyverse)
library(broom)
library(GGally)
body <- read_csv("https://dcgerard.github.io/stat_415_615/data/body.csv")
glimpse(body)
```

We always start with plots!

```{r}
ggpairs(body)
```

this only shows marginal relationships, not conditional relationships

midarm might still be associated with fat --\> seems less correlated --\> provides new info

triceps and thigh seem to provide the same info

let's calculate sums of squares:

where X1 is triceps, X2 is thigh, X3 is midarm, and Y is fat

```{r}
lm_all <- lm(fat ~ triceps + thigh + midarm, data = body)
```

you can get extra sum of squares by `anova()`:

```{r}
anova(lm_all)
```

SSR(x1) = 352 --\> how much of total variability explained by just X1

SSR(X2\|X1) = 33 --\> how much variability was NOT explained by X1 but CAN be explained by X2

SSR(X3\|X1, X2) = 12 --\> how much variability was explained by X3, controlling for X2

SSE(X1, X2, X3) = 98 --\> how much variability was NOT explained by any of the predictors

SSTO = 352 + 33 + 12 + 98

SSR(X1, X2) = 352 +33

SSE(X1) = 33 + 12 + 98

The above way of displaying the ANOVA table is called a Type 1 ANOVA table

```{r}
lm_all_2 <- lm(fat ~ thigh + midarm + triceps, data = body)
anova(lm_all_2)
```

this is a different anova decomposition --\> the order matters

SSR(X2) = 382

SSR(X3\|X2) = 2

SSR(X1\|X2, X3) = 13

SSE(X1, X2, X3) = 98

A Type II ANOVA table only shows you the extra sums of squares of a variable given all others

```{r}
library(car)
Anova(lm_all)
```

SSR(X1\|X2, X3) = 12.7

SSR(X2\|X1, X3) = 7.5

SSR(X3\|X1, X2) = 11.5

SSE(X1, X2, X3) = 98.4

these are only the extra sums of squares (conditional sums of squares)

# Application of F-Test

## Overall F-Test

use glance from the broom package

```{r}
glance(lm_all)
```

F-statistic = 21.52

df_extra = 3

p-value = 0.000007343 -\> we have strong evidence to reject H0 --\> we can conclude that there is strong evidence to suggest at least one of triceps, thigh, and midarm is associated with body fat (p-value of 0.000007343)

## F-test for one variable

You can use anova to get the single variable inculusion p-values for all variables

```{r}
Anova(lm_all)
```

The Sums of squares are extra sums of squares
