---
title: "r_visualization_review"
author: "lisa liubovich"
date: "2024-01-17"
output: pdf_document
url: "blue"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# options(repos = c(CRAN = "https://cloud.r-project.org/")) only need this if installing packages 
```

```{r}
library(ggplot2)
library(dplyr)
# ctrl alt I is insert code chunk
# message = FALSE inside the {r} will get rid of the messages that library(tidyverse) generates
```

## formatting

hyperlinks are included like this [Google] (<https://www.google.com>)

or we can include URLs directly like this <https://www.google.com>

# **visualization review (ggplot2)**

```{r}
data(mpg, package = "ggplot2")
glimpse(mpg)
```

## one variable

```{r}
#continuous
ggplot(data = mpg, mapping = aes(x = hwy, color = drv)) +
  geom_histogram()

ggplot(data = mpg, mapping = aes(x = hwy)) +
  geom_histogram(bins = 10, color = "black", fill = "white")
```

**Exercise**: Load in the [estate](https://dcgerard.github.io/stat_415_615/data/estate.csv) data (see [here](https://dcgerard.github.io/stat_415_615/data.html#real-estate-sales) for a description) and make a histogram of price with 20 bins. Make the bins red

```{r exercise}
estate <- read_csv(file = "./week_1/estate.csv")
```

```{r exercise}
ggplot(estate, mapping = aes(x = price)) +
  geom_histogram(bins = 20, color = "black", fill = "red")
```

```{r}
# discrete
ggplot(data = mpg, mapping = aes(x = drv)) +
  geom_bar()
```

-   **Exercise**: What variables from the estate data are appropriately plotted using a bar plot? Plot them.

```{r exercise}
ggplot(estate, mapping = aes(x = bed)) +
  geom_bar()
```

```{r exercise}
ggplot(estate, mapping = aes(x = bath)) +
  geom_bar()
```

```{r exercise}
ggplot(estate, mapping = aes(x = garage)) +
  geom_bar()
```

## two variables

```{r}
# continuous x and y
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() # this shows overlapping points; adjust with jitter

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_jitter() # adjusted for overlap

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

**Exercise**: Using the `estate` data, make a scatterplot of number of bedrooms versus number of bathrooms. Adjust for any overplotting.

```{r exercise}
ggplot(estate, mapping = aes(x = bed, y = bath)) +
  geom_jitter()
```

```{r}
# discrete X, continuous Y
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) +
  geom_boxplot()
```

-   **Exercise**: Using the `estate` data, plot sales price versus style. (*hint*: you need to first convert `style` to a factor using `as.factor()`)

```{r exercise}
estate <- estate %>% 
  mutate(style = as.factor(style))
```

```{r exercise}
ggplot(estate, mapping = aes(x = style, y = price)) +
  geom_boxplot()
```

## color coding

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy, color = drv)) +
  geom_jitter()
```

**Exercise**: Using the `estate` data, create a boxplot of price versus ac, color coding by pool

```{r exercise}
ggplot(estate, mapping = aes(x = ac, y = price, color = pool)) +
  geom_boxplot()
```

## changing a legend title

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy, color = drv)) +
  geom_jitter() +
  scale_color_discrete(name = "New Name1")
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy, shape = drv)) +
  geom_jitter() +
  scale_shape_discrete(name = "New Name2")
```

## faceting

You can facet by a categorical variable by adding a `facet_grid()` or `facet_wrap()` function

The variable to the left of the tilde ("`~`") indexes the row facets, the variable to the right of the tilde indexes the column facets. Using a dot ("`.`") in place of a variable means that there will only be one row/column facet.

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  facet_grid(. ~ drv)
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  facet_grid(drv ~ .)
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  facet_grid(fl ~ drv)
```

**Exercise**: Using the `estate` data, plot price versus area, faceting by ac, color coding by pool

```{r}
ggplot(estate, mapping = aes(x = price, y = area, color = pool)) +
  geom_point() +
  facet_grid(~ ac)
```

## change theme

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  theme_classic()
```
