---
title: "ANOVA"
author: "David Gerard"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(broom)
body <- read_csv("https://dcgerard.github.io/stat_415_615/data/body.csv")
glimpse(body)
```


```{r, message=FALSE}
library(GGally)
ggpairs(body)
```



Let's fit the regression of fat on midarm
```{r}
# install.packages("GGally")
lm_mid <- lm(fat ~ midarm, data = body)
a_mid <- augment(lm_mid)
sum(a_mid$.resid^2)
```

```{r}
lm_mid_thigh <- lm(fat ~ midarm + thigh, data = body)
a_mid_thigh <- augment(lm_mid_thigh)
sum(a_mid_thigh$.resid^2)
```

Let's make a Type I ANOVA Table
```{r}
lm_all <- lm(fat ~ triceps + thigh + midarm, data = body)
anova(lm_all)
```

SSR(X1) = 352
SSR(X2|X1) = 33
SSR(X3|X1,X2) = 12
SSE(X1, X2, X3) = 98

Question: How do I get SSTO?
SSTO = 352 + 33 + 12 + 98

You can get an ANOVA decomposition in a different order

```{r}
lm_all_2 <- lm(fat ~ thigh + midarm + triceps, data = body)
anova(lm_all_2)
```

X1 = triceps
X2 = thigh
X3 = midarm

SSR(X2) = 382
SSR(X3|X2) = 2
SSR(X1|X2, X3) = 13
SSE(X1, X2, X3) = 98

Often, more useful, are Type II sums of squares, provided by Anova() from car.
```{r}
library(car)
Anova(lm_all)
```
SSR(X1|X2, X3) = 12.7
SSR(X2|X1, X3) = 7.5
SSR(X3|X1, X2) = 11.5



Overall F-test in R is output via `glance()` in the broom package.

```{r}
lm_all <- lm(fat ~ triceps + thigh + midarm, data = body)
glance(lm_all)
```
F-statistic is 21.52
df-extra is 4 - 1 = 3
p-value for the F-test is 7.343e-06

We have strong evidence that at least one of triceps, thigh, and midarm are associated with fat.


To get the F-test results for one variable inclusions, use Anova() from car
```{r}
Anova(lm_all)
```

F-statistic for including triceps is 2.07, the df extra is 1, the p-value is 0.17

```{r}
tidy(lm_all)
```


To run an F-test  for inclusion of multiple variables, fit both the reduced and the full separately, then plug those into `anova()`.

```{r}
lm_full <- lm(fat ~ triceps + thigh + midarm, data = body)
lm_reduced <- lm(fat ~ triceps, data = body)
anova(lm_reduced, lm_full)
```

SSE(X1) = 143.1
SSE(X1, X2, X3) = 98.4
SSR(X2, X3 | X1) = 44.7
F-statistic = 3.64
p-value = 0.05

We have some evidence that at least one of thigh or midarm are associated with fat, adjusting for triceps (p = 0.05).




```{r}
earnings <- read_csv("https://dcgerard.github.io/stat_415_615/data/earnings.csv")
earnings <- mutate(earnings, log_earn = log(earn))
earnings <- select(earnings, log_earn, ethnicity, height)
earnings <- filter(earnings, is.finite(log_earn))
glimpse(earnings)
```


```{r}
ggpairs(earnings)
```



```{r}
lm_earn <- lm(log_earn ~ ethnicity + height, data = earnings)
tidy(lm_earn)
```

To test if a categorical variable is associated with Y (adjusting for others) use `Anova()`.

```{r}
Anova(lm_earn)
```

To change the base class, turn it into a factor and relevel.
```{r}
earnings <- mutate(earnings, ethnicity = factor(ethnicity))
earnings <- mutate(earnings, ethnicity = fct_relevel(ethnicity, "Hispanic"))
lm_earn <- lm(log_earn ~ ethnicity + height, data = earnings)
tidy(lm_earn)
```




```{r}
textile <- read_csv("https://dcgerard.github.io/stat_415_615/data/textile.csv")
glimpse(textile)
```

```{r}
ggpairs(textile)
```


You can tell if there are replicates by using 
```{r}
textile |>
  group_by(count, length) |>
  count()
```

To fit the reduced model, just run lm like usual
```{r}
lm_reduced <- lm(strength ~ count + length, data = textile)
```
To fit the full model, convert the predictors to factors, and fit lm by interaction terms.
```{r}
textile <- mutate(textile,
                  count_fac = factor(count),
                  length_fac = factor(length))
lm_full <- lm(strength ~ count_fac * length_fac, data = textile)
```

Use `anova()` to compare models
```{r}
anova(lm_reduced, lm_full)
```

You typically only use F-tests LOF for experimental designs where you put those replicates in there.

```{r}
anova(lm_all)
```

SSR(X1) = 352
SSR(X2|X1) = 33
SSR(X3|X1, X2) = 12
SSE(X1, X2, X3) = 98


SSE(X1) = 33 + 12 + 98
SSE(X1, X2) = 12 + 98
SSE(X1, X2, X3) = 98

$R^2_{Y1}$ = SSR(X1) / SSE(X1) = 352 / (352 + 33 + 12 + 98) = 0.71
$R^2_{Y2|1}$ = SSR(X2|X1) / SSE(X1) = 33 / (33 + 12 + 98) = 0.23
$R^2_{Y3|12}$ = SSR(X3|X1, X2) / SSE(X1, X2) = 12 / (12 + 98) = 0.11

Including tricepts reduces variability in body fat by 71%. Additionally including thigh results in an additional reduction of 23%. Including midarm results in an additional reduction of 11%.












